\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-04-05 paper.tex
Bump version: 0.1.4
Band Protocol introduction

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.3}
\begin{document}

@@

\newpage
\section{BAND Protocol}

>>>>

\title{\LARGE BAND\\
    \Large Unleashing Tokenized Economy}
\author{
        Soravis Srinawakoon\\
        \small\href{mailto:soravis@bandprotocol.com}
            {\nolinkurl{soravis@bandprotocol.com}}
    \and
        Sorawit Suriyakarn\\
        \small\href{mailto:swit@bandprotocol.com}
            {\nolinkurl{swit@bandprotocol.com}}
    }
\date{\today\\\small Draft Version 0.1.4}
\begin{document}

@@

\section{BAND Protocol}
BAND Protocol is a decentralized protocol to create tokenized marketplace and token-curated community using a set of built-in smart contracts. The protocol has been designed to maximize usability and real-world adoption of both the protocol and applications built on top. Community Managers can easily create their community and sell their tokenized products and services similar to how they would offer those products and services in the real world. Similarly, consumers can easily discover, join and participate in the communities of their interest. With open-source protocol, developers can easily create user-friendly applications on top of the protocol.

BAND Protocol aims to standardize the way community, marketplace, products and services can be offered using blockchain technology. Below is a standard set of contracts BAND Protocol offer and their interaction. More information for each contract is detailed in the subsequent sections.

\bigbreak
\begin{figure}[h]
    \centering
    \includegraphics[width=1\textwidth]{figures/protocol}
    \caption{Overview of BAND Protocol Layer and interactions between Community Manager and community member. Arrows represent transaction and function call while circles represent cryptographic tokens. A letter inside circle represents different type of token: B for BAND Token, C for Community Token, P for Product Token, and D for Discount Token.}
    \label{fig:bandlayer}
\end{figure}
